\acknowledgements{I would like to express gratitude to Professor 
Charles Weibel for his guidance, his generous support throughout 
the years, for the many invitations to conferences that broadened 
the scope of my understanding in motivic cohomology and motivic 
homotopy theory, for the countless hours of discussions that 
formed the backbone of much of this thesis, and for more countless
hours spent in the editing of this thesis. Without your help, none 
of my thesis will be possible. Many thanks to my committee members
--- Professors Lev Borisov, Anders Buch, and Daniel Grayson ---
for the careful proofreading that ensured the accuracy and integrity 
of this body of work. I would also like to thank Professors 
Fr\'ed\'eric D\'eglise, Bruno Kahn, and Pablo Palaez for giving me
various pointers that have guided me in the writing of this thesis.

I am deeply grateful to math department of Rutgers University at 
New Brunswick for their generous financial support, for the
many help they have given me over the years, and for making my
years as a graduate student a most wonderful experience.
I wish to thank my parents for teaching me the strength to overcome
the many challenges throughout my life. I am also fondly grateful 
to Denise Ichinco, who have warmed my heart with her love and 
encouragement. Last but not least, I would like to thank Glen 
Wilson, Howard Nuer, Edmund Karasiewicz, Zhuohui Zhang, Jaret 
Flores, Sjuvon Chung and so many other mathematicians at Rutgers 
--- unfortunately, too many to list here --- for the help, the 
drive, and the friendship that have taught me so much about 
mathematics, and above all, about being a good person.}
