\chapter{Introduction} 

The goal of this thesis is to show that the abelian categories 
$\HI$ of homotopy invariant Nisnevich sheaves with transfers and 
$\CycMod$ of Rost's cycle modules each admits two filtrations. 
Here, a (weak) filtration of a category roughly means a nested sequence of 
subcategories together with reflection or coreflection functors 
from the category to each of its subcategories. The filtrations 
are induced by the slice filtration on the tensor triangulated 
category $\DMeff$ of Voevodsky's derived category of motive. One 
of the key ingredients in constructing the three filtrations is a 
sequence of adjoint functors from $\HI$ to itself, coming from the 
triangulated tensor structure of $\DMeff$. The other key 
ingredient is torsion theory.
 
We first revisit the basic definition and results of classical 
torsion theory for well-powered abelian categories, as developed 
in \cite{BJV} or \cite{DTor} (Chapter 2). However, instead of focusing
on the relationship between torsion theories and radicals, we
introduce the theory from the perspective of coradicals, which are 
radicals in the opposite category.  

We then summarize the theory in motivic cohomology needed to 
understand the tensor triangulated structure on $\DMeff$ 
(Chapters 3 and 4). These are taken from early lectures in 
\cite{MVW}. The main results that we highlight in these two 
chapters are the Cancellation Theorem of Voevodsky and the
existence of an object $\Z(1)$ of $\DMeff$ which gives rise to a pair of 
adjoint endofunctor on $\DMeff$. 

These results provide the necessary scaffold to introduce the 
slice filtration on $\DMeff$. The term ``slice filtration'' is the
name of a filtration structure on the stable homotopy category 
of motives that Voevodsky defined in \cite{VOP}. The analogous
structure for $\DMeff$ is constructed by Huber and Kahn in 
\cite{HuKa}. We summarize the main properties of the slice 
filtration on $\DMeff$ in Chapter 5, and develop an extension of
the slice filtration to the category $\DM$, which is the
triangulated category obtained from $\DMeff$ by inverting the
Tate motive (see Section \ref{sect_slice_filt_on_DM}).

In Chapter 6, we develop several filtrations on
$\HI$. We first note that $\DMeff$ is equipped with a 
$t$-structure in the sense of \cite{BBD}, and that $\HI$ is categorically
equivalent to the heart. An obvious question to ask is whether the
filtration structure on $\DMeff$ induces a similar structure on
$\HI$. In fact, the slice filtration on $\DMeff$ does induce two
filtrations on $\HI$. In addition, the reflection functors from
one of the filtrations define a sequence of coradicals. Applying
the results of Chapter 2, we obtain a third filtration, which has
the additional property that the filtration on $\HI$ induces a 
functorial filtration of each object of $\HI$. We coin the
term ``torsion filtration'' to describe the filtrations that
come from a sequence of coradicals.

We then extend the torsion
filtrations on $\HI$ to the abelian category $\HI_*$ of homotopy 
modules (Chapter 7). The key is to construct a $\Z$-indexed sequence
of coradicals on $\HI_*$. Once we have accomplished this, applying
the results of Chapter 2, we obtain filtrations of $\HI_*$. Using 
the fact that $\HI_*$ is categorically equivalent to $\CycMod$, we 
conclude that these filtrations exist on $\CycMod$. 

In the last chapter, we summarize the results of the previous 
chapters by axiomatizing the conditions on a triangulated with a 
$t$-structure such that the heart is equipped with a sequence of 
coradicals whose associated torsion theories form two filtrations 
on the category. The essential ingredient is for a tensor 
triangulated category with a $t$-structure to be equipped with a 
Tate object --- an object $S$ in the heart such that the functor 
given by tensoring with $S$ admits a right adjoint --- such that 
the Cancellation Theorem holds for $S$. We call such a 
triangulated category \emph{torsion monoidal}, and we show that 
the heart of any torsion monoidal category is equipped with three 
filtrations, two of which are induced by a sequence of coradicals.

For the remainder of the thesis, we assume that $\basefield$ is
a perfect field.
